
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/r-lib/pingr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/pingr/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-lib/pingr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-lib/pingr?branch=main)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/pingr)](https://r-pkg.org/pkg/pingr)
<!-- badges: end -->

# pingr: check if a server is alive

The pingr package has tools to check if a remote computer or web server is
up and some other related tools.

## ICMP ping

The `ping()` function does ICMP ping, via the system's `ping` utility:

```{r}
library(pingr)
ping("127.0.0.1")
```

By default it sends three packets and measures the time it receives and answer.
It waits between sending out the packets, so if you want a really quick check,
you can just send a single packet:

```{r}
ping("127.0.0.1", count = 1)
```

If a machine is down (or it does not exist), then `NA` is returned instead
of the roundtrip time:

```{r}
ping("192.0.2.1", count = 1)
```

## TCP ping

With TCP ping we can check if a machine is listeing on a TCP port, e.g. if
google's search web server is up and running:

```{r}
ping_port("www.google.com", port = 80, count = 1)
```

## Query the public IP address of the computer

`my_ip()` queries the public IP of the computer, either via DNS or HTTPS:

```{r}
my_ip()
```

## Check if the computer is online

`is_online()` checks if the computer is online. It makes three tries:

* Queries myip.opendns.com on OpenDNS, see `my_ip()`.
* Retrieves icanhazip.com via HTTPS, see `my_ip()`.
* Retrieve Apple's Captive Portal test page, see `apple_captive_test()`.

If any of these are successful, it returns `TRUE`.

```{r}
is_online()
```

## DNS queries

The package also contains a function to perform DNS queries. This is a
more portable and more functional version of the `utils::nsl()` function:

```{r}
nsl("www.r-project.org", type = 1L)
nsl("google.com", type = 28L)
```

## License

MIT © RStudio
